\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-27 pldi/draft.tex
Small fixes in unix50 and the discussion of one-liners

No Eager and Blocking Eager depict configurations without \sys's \ttt{eager} optimization and without \ttt{split}. These configurations perform worse than \sys with \ttt{eager} in all cases (except for a negligible difference in shortest-scripts) for the reasons described in \Cref{optimizer}. Adding \ttt{split} on top of that (Par + Split, Par + B. Split) further improves speedup for some scripts that have \tpur or \tnpu commands, and for the rest it does not affect performance. Finally, the optimized bi-grams script achieves significantly more benefits from \sys than its unoptimized counterpart, showing that familiarity with \sys's parallelizability classes goes a long way in terms of performance.

@@

%% \TODO{An important point that needs to be made clear is that these are
%%   taken from the wild unmodified. And that Pash never leads to
%%   slowdown (except for the trivial head cases, where the slowdown is
%%   neligible).}
\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{ours}, Discussion).
Their input was generated by multiplying their original input several times, enough to reach 10GB.
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all 34 pipelines.
(\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is $5.49\times$, median is $6.07\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

\heading{Discussion}
Most pipelines see significant acceleration, except 13, 24, 25, 26, 29, 30 that see no speedup and 2, 19, 31 that see a slowdown.
The first group contains commands which \sys cannot parallelize without risking breakage---\eg \ttt{awk} and \ttt{sed} \ttt{-d}. % and \ttt{tr} \ttt{-d}.
Some of them use general interpreters when they could be using a specialized equivalent tailored to the task at hand, the typical example being \ttt{awk} vs \ttt{cut}.
By attempting only such obvious (to us, experts) replacements, \sys extracts further parallelism---\eg 13 sees a 8.1$\times$ speedup.
% ---a common pattern we witnessed~\sx{macro1}.

>>>>

No Eager and Blocking Eager depict configurations without \sys's \ttt{eager} optimization and without \ttt{split}. As described in \Cref{optimizer}, these configurations perform worse than \sys with \ttt{eager} in all cases (except for a negligible difference in shortest-scripts). Adding \ttt{split} on top of that (Par + Split, Par + B. Split) further improves speedup for some scripts that have \tpur or \tnpu commands, and for the rest it does not affect performance. Finally, the optimized bi-grams script achieves significantly more benefits from \sys than its unoptimized counterpart, showing that familiarity with \sys's parallelizability classes could go a long way in terms of performance.

@@

%% \TODO{An important point that needs to be made clear is that these are
%%   taken from the wild unmodified. And that Pash never leads to
%%   slowdown (except for the trivial head cases, where the slowdown is
%%   neligible).}
\heading{Results}
\sys's parallelism is set to $16\times$, as many of these pipelines are relatively long (\S\ref{ours}, Discussion).
Their input was generated by multiplying their original input several times, enough to reach 10GB.
Fig.~\ref{fig:unix50-individual} shows the speedup (left) over the sequential runtime (right) for all 34 pipelines. We use the pipeline index to refer to them in both plots and discussion.
%% (\nv{Pipelines are referred by number, in both the plot and the discussion below.})
Average speedup is $5.49\times$, median is $6.07\times$, and weighted average (with the absolute times as weights) is $5.75\times$.
 % the \todo{geometric mean is $1.08\times$},

@@

\heading{Discussion}
Most pipelines see significant acceleration, except 13, 24, 25, 26, 29, 30 that see no speedup and 2, 19, 31 that see a slowdown.
The first group contains commands which \sys cannot parallelize without risking breakage---\eg \ttt{awk} and \ttt{sed} \ttt{-d}. % and \ttt{tr} \ttt{-d}.
Note however, that some of the pipelines contain more general commands that cannot be parallelized since they were not written with that goal in mind; a common example is the use of \ttt{awk} for reordering or removing columns of the input.
%% Some of them use general interpreters when they could be using a specialized equivalent tailored to the task at hand, the typical example being \ttt{awk} vs \ttt{cut}.
In particular, replacing an \ttt{awk} that was just used to sort on the second field \ttt{awk "{print \$2, \$0}" | sort -nr} with a single \ttt{sort -nr -k 2} in the 13th pipeline allows \sys to achieve 8.1$\times$ speedup (in contrast to the original 1.01$\times$).
%% , attempting only such obvious (to us, experts) replacements, \sys extracts further parallelism---\eg 13 sees a 8.1$\times$ speedup.
% ---a common pattern we witnessed~\sx{macro1}.
